For submission to the Journal of Integrated Pest Management

### 2021-06-16 ofv_fife_2021.Rmd
forgot to update the figure captions with the correct plant IDs, as verified by Dr. Hale

### Figure captions
`r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by *Liriope* spp. infected with *Orchid fleck dichorhavirus*: (a) ringspot symptoms on *Liriope gigantea* (b-c) Details of ringspot symptoms on *Liriope gigantea* (d) chlorotic ringspot *Liriope muscari* cv. 'Silvery Sunproof'")`

>>>>

### Figure captions
`r fig_nums(name = "fig_1", caption = "Variety of symptoms expressed by *Liriope* spp. infected with *Orchid fleck dichorhavirus*: (a) ringspot symptoms on *Liriope muscari* cv. 'Gigantea' (b-c) Details of ringspot symptoms on *L. muscari* cv. 'Gigantea' (d) rust colored spots on *Ophiopogon intermedius*")`
